Continuously Generalizing Buildings to Built-up Areas\\ by Aggregating and Growing

### 2017-09-21 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved case study and conclusion

@@

\subsection{Eliminating small buildings}
\label{sec:Eliminate}
Following the previous steps of continuous generalization may result in the 
creation of small isolated building aggregates that do not belong to the goal 
map polygon because of their isolation.
That is why we eliminate a building aggregate if the area of this building is 
smaller than a threshold.
Following \citet{Stoter2009} and \citet{Chaudhry2008}, 
we set this threshold as $a=0.16\,\mathrm{mm}^2$ on map.
The real threshold at time $t$ is
\[
a_t=a\cdot M_t^2.
\]
For a group of buildings that will be aggregated into one built-up area at time 
$t=1$, we consider the area sum of all the buildings at time $t$, 
instead of considering each building individually.

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
The offsetting function and clipping function are from library \textsc{Clipper} 
of \citet{Johnson2014}.
The offsetting function realizes 
our operations of buffering, dilating, eroding, and merging.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
\fig\ref{fig:Data} shows our testing data, 
which is from the French Mapping Agency (IGN).
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns (communes in French), 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques department, south-western France.

@@

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
The $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left if we simplify using
the Douglas--Peucker algorithm.

We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
This production cost $668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:GoalShape}.
We counted the numbers of buildings in our results,
and compared our numbers to the numbers calculated by T\"opfer's radical law
(see \fig\ref{fig:BuilidngNumber}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966}, we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
As a result, we computed the number according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where $n_s=2{,}590$ is the number of buildings on start map
and $n_t$ is the number of buildings on a map at scale $1:M_t$.
According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data from IGN at scale $1:50{,}000$.
No small buildings are removed in our result or the IGN data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to make a more convincing comparison.

@@

@@

It is always interesting to know what is the quantity we should keep on a map.
We compared the number of buildings between our results and the calculated 
numbers from T\"opfer's radical law.
It turned out that our numbers decreased too fast.
We may also take into account the fractal law of \citet{Jiang2015}.
Another interesting problem is to compare the area of the buildings.

>>>>

\todo{not intersecting buildings from a previous step?}

@@

\subsection{Eliminating small buildings}
\label{sec:Eliminate}
Following the previous steps of continuous generalization may result in the 
creation of small isolated building aggregates that do not belong to the goal 
map polygon because of their isolation.
That is why we eliminate a building aggregate if the area of this building is 
smaller than a threshold.
Following \citet{Stoter2009} and \citet{Chaudhry2008}, 
we set this threshold as $a=0.16\,\mathrm{mm}^2$ on map.
The real threshold at time $t$ is
\[
a_t=a\cdot M_t^2.
\]
For a group of buildings that will be aggregated into one built-up area at time 
$t=1$, we consider the area sum of all the buildings at any time $t$, 
instead of considering each building individually.

@@

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
The offsetting function and clipping function 
are available from library \textsc{Clipper} of \citet{Johnson2014}.
The offsetting function realizes 
our operations of buffering, dilating, eroding, and merging.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
Our testing data is from the French Mapping Agency (IGN);
see \fig\ref{fig:Data}.
The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
It represents the buildings of four towns, 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques department, south-western France.
IGN also stores a dataset at scale $1:50{,}000$.
This dataset was basically obtained from the data at scale $1:15{,}000$ 
by buffering with distance $25\,\mathrm{m}$.
Sometimes distance $50\,\mathrm{m}$ was also used when buffering
in order to identify towns.
A town is defined by \citet{Boffet2000} that the longest edge in an MST of the 
buildings should be shorter than $100\,\mathrm{m}$.

@@

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
The $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left when we simplified using
the Douglas--Peucker algorithm.

We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
This production cost $668.2\,\mathrm{s}$ in total.
We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
the marked region in \fig\ref{fig:GoalShape}.
We counted the numbers of buildings in our results,
and compared our numbers to the numbers calculated by T\"opfer's radical law
(see \fig\ref{fig:BuilidngNumber}).
We have unexaggerated-area symbols, 
so for \eq2 of \citet{Topfer1966} we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
As a result, we computed the numbers according to
\[
n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
\]
where $n_s=2{,}590$ is the number of buildings on start map
and $n_t$ is the number of buildings on a map at scale $1:M_t$.
According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
the numbers from the radical law.
It seems that our result supports the fractal law proposed by \citet{Jiang2015}.

\begin{figure}[tb]
	\centering
	\begin{tikzpicture}[]
	\begin{axis}[
	height=5cm,
	width= \linewidth-0.1cm,
	axis lines = left,
	%	axis x line=center,
	%	axis y line=left,
	xtick={0.1,0.2,...,1},
	ytick={500,1000,...,3000},
	xlabel={$t$},
	ylabel={number of buildings},
	xlabel style={below right},
	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
	xlabel style={at={(axis description cs:1,0)},anchor=north},
	%	ylabel style={above left},
	xmin=0,
	xmax=1.1,
	ymin=0,
	ymax=3200,
	cycle list name=black white,
	]
	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
%	\addplot+ [domain=0:1,samples=11] {2590* (15/(15+35* x))^1.5};
	\addplot+  coordinates {
		(0,2590)
		(0.1,1963)
		(0.2,758)
		(0.3,304)
		(0.4,177)
		(0.5,122)
		(0.6,92)
		(0.7,73)
		(0.8,66)
		(0.9,59)
		(1,56)		
	};
	\legend{\quad radical law, \quad our results}
	\end{axis}
	\end{tikzpicture}
	\caption{A comparison of the numbers of building between our results and 
		T\"opfer's radical law.}
	\label{fig:BuilidngNumber}
\end{figure}

\fig\ref{fig:ExperimentalComparison} shows a comparison of 
our result at time $t=1$
and the data at scale $1:50{,}000$.
No small building is removed in our result or the existing data.
The boundaries of our built-up areas are more straight than that of IGN data, 
where we have $1{,}135$ edges while the data has $4{,}968$ edges.
From this perspective, we would say that our result is 
more reasonable than the existing data.
A questionnaire, however, is needed to make a more convincing comparison.

@@

%\section{Case Study}
%\label{sec:CaseStudy}
%We have implemented our method based on
%C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
%The offsetting function and clipping function are from library 
%\textsc{Clipper} 
%of \citet{Johnson2014}.
%The offsetting function realizes 
%our operations of buffering, dilating, eroding, and merging.
%An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
%We ran our case study under 64-bit 
%Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
%We measured processing time by the built-in C\# class 
%\emph{Stopwatch}.
%\fig\ref{fig:Data} shows our testing data, 
%which is from the French Mapping Agency (IGN).
%The data is at scale $1:15{,}000$, which means $M_\mathrm{s}=15{,}000$.
%It represents the buildings of four towns (communes in French), 
%i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
%in the Pyr\'en\'ees-Atlantiques department, south-western France.
%
%We set our goal scale at $1:50{,}000$, which means $M_\mathrm{g}=50{,}000$,
%and $d_\mathrm{G}=25\,\mathrm{m}$
%so that we can compare our result with the exiting data.
%Also, this setting makes \eq\ref{eq:S_g} hold, 
%where $l=0.3\,\mathrm{mm}$.
%In \eq\ref{eq:d_Dt}, the first part is always smaller than the second part 
%according to our settings.
%As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
%where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
%according to \eq\ref{eq:d_Et} and $\alpha=1.5$.
%
%Our program took $93.6\,\mathrm{s}$ 
%to compute the goal shapes of the built-up areas.
%\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
%The $56$ built-up areas have $2{,}095$ edges before line simplification.
%Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
%In comparison, there are $1{,}597$ edges left if we simplify using
%the Douglas--Peucker algorithm.
%
%\begin{figure}[tb]
%	\centering
%	\includegraphics{Data}
%	\caption{Data.
%		There are $2{,}590$ buildings, 
%		which in total have $19{,}255$ edges and have area
%		$448{,}996.8\,\mathrm{m}^2$.}
%	\label{fig:Data}
%\end{figure}
%
%
%We produced a sequence of $10$ maps, i.e., $t \in \{0.1, 0.2, \dots, 1\}$.
%This production cost $668.2\,\mathrm{s}$ in total.
%We show such a sequence of maps in \fig\ref{fig:ContinuousGeneralization} for 
%the marked region in \fig\ref{fig:GoalShape}.
%We counted the numbers of buildings in our results,
%and compared our numbers to the numbers calculated by T\"opfer's radical law
%(see \fig\ref{fig:BuilidngNumber}).
%We have unexaggerated-area symbols, 
%so for \eq2 of \citet{Topfer1966}, we used $C_\mathrm{b2}$ and $C_\mathrm{z3}$.
%As a result, we computed the number according to
%\[
%n_t=n_\mathrm{s}\frac{M_\mathrm{s}}{M_t},
%\]
%where $n_s=2{,}590$ is the number of buildings on start map
%and $n_t$ is the number of buildings on a map at scale $1:M_t$.
%According to \fig\ref{fig:BuilidngNumber}, our numbers decrease faster than 
%the numbers from the radical law.
%It seems that our result supports the fractal law proposed by 
%\citet{Jiang2015}.
%
%
%
%\begin{figure}[tb]
%	\centering
%	\begin{tikzpicture}[]
%	\begin{axis}[
%	height=5cm,
%	width= \linewidth-0.1cm,
%	axis lines = left,
%	%	axis x line=center,
%	%	axis y line=left,
%	xtick={0.1,0.2,...,1},
%	ytick={500,1000,...,3000},
%	xlabel={$t$},
%	ylabel={number of buildings},
%	xlabel style={below right},
%	%	ylabel style={at={(axis description cs:0,1.1)},rotate=270,anchor=north},
%	xlabel style={at={(axis description cs:1,0)},anchor=north},
%	%	ylabel style={above left},
%	xmin=0,
%	xmax=1.1,
%	ymin=0,
%	ymax=3200,
%	cycle list name=black white,
%	]
%	\addplot+ [domain=0:1,samples=11] {2590*15/(15+35* x)};
%	\addplot+  coordinates {
%		(0,2590)
%		(0.1,1963)
%		(0.2,758)
%		(0.3,304)
%		(0.4,177)
%		(0.5,122)
%		(0.6,92)
%		(0.7,73)
%		(0.8,66)
%		(0.9,59)
%		(1,56)		
%	};
%	\legend{\quad radical law, \quad our results}
%	\end{axis}
%	\end{tikzpicture}
%	\caption{A comparison of the numbers of building between our results and 
%		T\"opfer's radical law.}
%	\label{fig:BuilidngNumber}
%\end{figure}
%
%\fig\ref{fig:ExperimentalComparison} shows a comparison of 
%our result at time $t=1$
%and the data from IGN at scale $1:50{,}000$.
%No small buildings are removed in our result or the IGN data.
%The boundaries of our built-up areas are more straight than that of IGN data, 
%where we have $1{,}135$ edges while the data has $4{,}968$ edges.
%From this perspective, we would say that our result is 
%more reasonable than the existing data.
%A questionnaire, however, is needed to make a more convincing comparison.
%
%%Our result at time $t=1$ have area $4{,}121{,}028.2\,\mathrm{m}^2$.
%
%
%
%\begin{figure*}[tb]
%	\centering
%	\includegraphics{GoalShape}
%	\caption{Bridged original buildings 
%		and goal shapes of the built-up areas (without removing small holes), 
%		at scale $1:50{,}000$.
%		There are $56$ built-up areas, which have $1{,}102$ edges in total.
%		We show a sequence of maps in \fig\ref{fig:ContinuousGeneralization} 
%		for the region marked by the dashed circle.
%	}
%	\label{fig:GoalShape}
%\end{figure*}
%
%\begin{figure*}[tb]
%	\centering
%	\includegraphics{ContinuousGeneralization}
%	\caption{A sequence of maps at time $t \in \{0, 0.1, 0.2, \dots, 1\}$
%		for the region marked in \fig\ref{fig:GoalShape}.
%	}
%	\label{fig:ContinuousGeneralization}
%\end{figure*}
%
%\begin{figure*}[tb]
%	\centering
%	\includegraphics{ExperimentalComparison}
%	\caption{A comparison of our result and the existing data at scale 
%	$1:50{,}000$.
%		The brighter gray polygons represent the original buildings.
%		The darker gray polygons are our result at time $t=1$.
%		The gray polylines represent the data of the built-up areas at scale 
%		$1:50{,}000$ from IGN, where some built-up areas are split because some 
%		streets cross these areas.
%	}
%	\label{fig:ExperimentalComparison}
%\end{figure*}
%
%
%%The area on start map is $some number\,\text{mm}^2$.
%%Our area on map is $some number\,\text{mm}^2$.
%%According to \eq4 of paper \citet{Topfer1966}, 
%%the area on map should be $some number\,\text{mm}^2$
%
%%Although a version with a 
%%lower running time exists \citep[see][]{Chan1992}, we implemented the basic 
%%version

@@

It is always interesting to know what is the quantity we should keep on a map.
We compared the numbers of buildings of our results 
with the numbers calculated by T\"opfer's radical law.
It turned out that our numbers decreased too fast.
We may also take into account the fractal law of \citet{Jiang2015}.
Another interesting problem is to compare the area of the buildings.
